\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} 
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
    a4paper,
    top=1.8cm,
    bottom=1in,
    left=2.5cm,
    right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=2em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}
\usepackage[dvipsnames]{xcolor}
\colorlet{icnclr}{gray}
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\fontseries{bold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\color{gray}\fontseries{bold}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}

\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							

\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

%== HEADER ==%
\begin{center}      
    {\fontsize{28}{28}\selectfont Pham Huy Duc} \\ \bigskip

    {\color{icnclr}\faMapMarker} Da Lat City, Lam Dong, Vietnam \quad 
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:rei.jin.71@gmail.com}{rei.jin.71@gmail.com} \quad
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:+840342566825}{+84 0342566825}
\end{center}
%==============

\section{About Me}
Coffee, coding, and problem-solving are my passions. I love using Golang for its simplicity and ease in building large systems.

%==============
\section{Work Experience}

\subsection{Backend Developer \hfill \normalfont Jun 2023 - June 2024}
\subsubsection{DOIT Solutions, Vietnam}
\begin{itemize}
    \item[\checkmark] Designed and structured a production optimization system for a biology lab using Domain-Driven Design (DDD).
    \item[\checkmark] Implemented Redis caching and task scheduling for background processes.
    \item[\checkmark] Developed a real-time error tracking and notification system.
    \item[\checkmark] Collaborated closely with frontend developers using Vue.js to ensure seamless integration.
\end{itemize}

\subsection{Intern \hfill \normalfont Mar 2023 - Jun 2023}
\subsubsection{DOIT Solutions, Vietnam}
\begin{itemize}
    \item[\checkmark] Contributed to warehouse management feature design and implementation for an agricultural enterprise.
    \item[\checkmark] Developed frontend features using Vue.js and built RESTful APIs with Gin.
    \item[\checkmark] Optimized database queries with Gorm and MySQL to improve system performance.
    \item[\checkmark] Wrote unit tests and created command-line tools for backend support.
\end{itemize}

%==============
\section{Honors \& Awards}
\begin{itemize}
    \item[\checkmark] Third place in the Lam Dong startup competition for developing a software to manage biology lab processes.
\end{itemize}

%==============
\section{Skills}
\subsection{Programming Languages}
\begin{itemize}
    \item[\checkmark] \textbf{Golang}: Extensive experience building backend systems and RESTful APIs.
    \item[\checkmark] \textbf{Vue.js}: Built dynamic user interfaces for web applications.
    \item[\checkmark] \textbf{Gin}: Developed secure and high-performance web services.
    \item[\checkmark] \textbf{MySQL}: Designed, optimized, and managed databases for production environments.
\end{itemize}

\subsection{Tools \& Technologies}
\begin{itemize}
    \item[\checkmark] \textbf{Redis}: Implemented caching for efficient task processing and reduced latency.
    \item[\checkmark] \textbf{Gorm}: Optimized complex database queries for higher performance.
    \item[\checkmark] \textbf{Git}: Version-controlled projects with an emphasis on collaboration.
\end{itemize}

%==============
\section{Certifications \& Awards}
\begin{itemize}
    \item[\checkmark] Third place, Lam Dong startup competition (2023)
    \item[\checkmark] Certification Link: \href{https://explorer.perawallet.app/asset/2255455434/}{Blockchain Asset on PeraWallet}
\end{itemize}

\end{document}
